---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  margin-top: 50px;
  margin-bottom: 50px;
  max-width: fit-content;
  margin-inline: auto;
}

.uline {
  text-decoration: underline;
}
```

## Multi-Platform Advertisement Interaction

<p class = "uline">***Purpose:***</p>

This report looks at the types of advertisements observed across various 
platforms and the interactions with them. 

The data was collected through observational logging.



```{r}

# Setup

library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSv0fWW7g88VCzcYOgfHWKOUhj4WfkzCwnJSfSTinA4iSUIoW42znk4u86luNA9de59NnlVsAbtnUzv/pub?gid=122816818&single=true&output=csv")


# Renaming Variables for clarity
latest_data <- logged_data %>%
                      rename(Platform = 2,
                            Category = 3,
                            Ad_Length = 4,
                            Did_Interact = 5,
                            How_Interact = 6
                            )


# ********** Chosen Data **********
  
# Summary Value 1 - Category Totals
cat_total <- count(latest_data, Category)

# Summary Value 2 - Platform Totals
platform_total <- count(latest_data, Platform)

# Summary Value 3 - Mean Advertisement Length
mean_length <- latest_data$Ad_Length %>% mean() %>% round(2)

# Summary Value 4 - Total Advertisements
total_data <- nrow(latest_data)


```

<p class = "uline">***Dynamic Facts:***</p>

- A total of ***`r total_data`*** advertisements were recorded.

- The mean advertisement length is ***`r mean_length`*** seconds.


## Dynamic Graphs

### Advertisements by Category

```{r}
# Chart 1 - Advertisements by Category
latest_data %>%
  ggplot() +
  geom_bar(aes(x = Category),
           fill = "#ADD8E6") +
  labs(title = "Plot of Advertisement Categories",
       x = "Category",
       y = "Count")

```


### Advertisements by Platform

```{r}
# Chart 2 - Advertisements by Platform
latest_data %>%
  ggplot() +
  geom_bar(aes(x = Platform),
           fill = "#88E788") +
  labs(title = "Plot of Advertisement Platforms",
       x = "Platform",
       y = "Count")

```


### Advertisement Interactions

```{r}
# Chart 3 - Advertisement Interactions
latest_data %>%
  # Splitting multiple selections up
  separate_rows(How_Interact, sep = ", ") %>%
  # Removing NA values
  drop_na() %>%
  ggplot() +
  geom_bar(aes(x = How_Interact),
           fill = "#CBC3E3") +
  labs(title = "Plot of Advertisement Interaction Types",
       x = "Interaction Types",
       y = "Count")
```


